\documentclass[10pt,letterpaper]{article}

\usepackage[
  top=0.5in,
  bottom=0.5in,
  left=0.65in,
  right=0.65in
]{geometry}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

\definecolor{accent}{HTML}{1F4E8C}
\definecolor{muted}{HTML}{555555}
\definecolor{dark}{HTML}{1A1A1A}

\hypersetup{colorlinks=true, urlcolor=accent}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{
  leftmargin=11pt, nosep, topsep=2pt, itemsep=1pt,
  label=\small$\circ$
}

\titleformat{\section}{\bfseries\small\color{accent}}
  {}{0pt}{\MakeUppercase}[\vspace{1pt}{\color{dark}\titlerule[0.4pt]}\vspace{1pt}]
\titlespacing{\section}{0pt}{6pt}{3pt}

\newcommand{\roleheading}[2]{%
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{\small\color{dark}#1} & \small\textcolor{muted}{#2}
  \end{tabularx}\vspace{-1pt}\par
}
\newcommand{\orgline}[2]{%
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textit{\footnotesize\textcolor{muted}{#1}} &
    \textit{\footnotesize\textcolor{muted}{#2}}
  \end{tabularx}\vspace{1pt}\par
}
\newcommand{\toolsline}[1]{%
  \textit{\footnotesize\textcolor{muted}{#1}}\vspace{2pt}\par
}
\newcommand{\skillrow}[2]{%
  \noindent{\footnotesize\textbf{#1:} #2}\par\vspace{1pt}
}

\begin{document}

% ── HEADER ────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\textbf{Jonathan Abhishek Rao Thota}}\\[4pt]
  \small\textcolor{muted}{%
    Houston, TX \;$|$\;
    \href{tel:+12055030985}{+1 205-503-0985} \;$|$\;
    \href{mailto:jonathanrao5576@gmail.com}{jonathanrao5576@gmail.com} \;$|$\;
    \href{https://jonathanthota.vercel.app}{jonathanthota.vercel.app}
  }\\[2pt]
  \small\textcolor{muted}{%
    \href{https://linkedin.com/in/jonathanrao99}{linkedin.com/in/jonathanrao99} \;$|$\;
    \href{https://github.com/jonathanrao99}{github.com/jonathanrao99} \;$|$\;
    \textit{OPT Authorized}
  }
\end{center}

\vspace{-14pt}

% ── PROFESSIONAL SUMMARY ───────────────────────────────────────────
\section{Professional Summary}

\footnotesize
M.S. Data Science graduate from Texas A\&M University--Victoria with proven expertise in building machine learning systems and backend services for real-world applications. Proficient in Python, REST APIs, and ML frameworks, with hands-on experience in model deployment, data pipelines, and scalable systems. Demonstrated ability to support the development, implementation, and testing of statistical models, integration of NLP, and refinement of prototypes. Committed to improving the intake process for the Mississippi Department of Child Protective Services using natural language processing and machine learning methods.

% ── SKILLS ────────────────────────────────────────────────────────
\section{Technical Skills}

\skillrow{Data Analysis}{EDA, Data Cleaning, Feature Engineering, Statistical Analysis, A/B Testing, KPI Tracking}
\skillrow{Machine Learning}{Regression, Classification, Time Series (LSTM), Model Evaluation, Cross-Validation}
\skillrow{Languages}{Python, SQL, R, JavaScript}
\skillrow{Data Tools}{Pandas, NumPy, Scikit-learn, TensorFlow, XGBoost}
\skillrow{Visualization}{Tableau, Power BI, Plotly, Matplotlib, Seaborn, Streamlit}
\skillrow{Data Engineering}{ETL Pipelines, Data Warehousing Concepts, REST APIs, PostgreSQL, MySQL}
\skillrow{GenAI}{LangChain, OpenAI API, RAG Pipelines, Prompt Engineering}
\skillrow{Tools}{Git/GitHub, Docker, Vercel, Jupyter Notebook, Colab}

% ── EXPERIENCE ────────────────────────────────────────────────────
\section{Experience}

\roleheading{Machine Learning Engineering Intern}{Aug 2023 -- Oct 2023}
\orgline{CodeClause}{Hyderabad, India}
\begin{itemize}\footnotesize
  \item Built an MRI brain tumor classifier using MobileNetV2 and transfer learning, achieving \textbf{86.6\%} accuracy with documented, reproducible methodology.
  \item Developed a real-time computer vision pipeline in Python and OpenCV for live video pattern detection, achieving \textbf{>85\%} accuracy at low latency.
  \item Fine-tuned a CNN-based age and gender detection model using transfer learning, improving inference speed by \textbf{35\%} and collaborating across a distributed team via GitHub.
\end{itemize}

\vspace{3pt}

\roleheading{Data Analyst \& ML Systems Developer}{Oct 2025 -- Jan 2026}
\orgline{Birdside HTX}{Houston, TX}
\begin{itemize}\footnotesize
  \item Designed and deployed scalable backend services using REST APIs to handle multi-source data ingestion, improving reliability and reducing operational errors by \textbf{70\%+}.
  \item Wrote Python pipelines to pull and clean multi-source datasets, applying statistical analysis and EDA to surface KPI trends with full documentation for handoff.
  \item Structured data workflows with modular components resembling microservice patterns, enabling easier scaling and maintenance.
\end{itemize}

\vspace{3pt}

\roleheading{Full Stack Developer}{Apr 2025 -- Dec 2025}
\orgline{Sol3 Studio}{Houston, TX}
\begin{itemize}\footnotesize
  \item Designed REST API integrations and automated data workflows with schema validation and transformation logic across multiple client platforms.
  \item Maintained version-controlled codebases in Git/GitHub and configured CI/CD deployments on Vercel for several production client projects.
\end{itemize}

% ── PROJECTS ──────────────────────────────────────────────────────
\section{Projects}

\roleheading{LLM-Based Data Assistant}{\href{https://github.com/jonathanrao99}{GitHub}}
\toolsline{Python, OpenAI API, LangChain, Retrieval-Augmented Generation}
\begin{itemize}\footnotesize
  \item Built an LLM-powered assistant to query structured datasets using natural language, enabling dynamic retrieval of insights across tabular data sources.
  \item Implemented embedding-based retrieval and context injection pipelines, improving response accuracy by \textbf{25\%} and reducing hallucinations in generated outputs.
  \item Designed modular RAG pipelines using LangChain to handle query processing, retrieval, and response generation.
\end{itemize}

\vspace{2pt}

\roleheading{Brain Tumor Detection -- Deep Learning Pipeline}{\href{https://github.com/jonathanrao99}{GitHub}}
\toolsline{Python, TensorFlow/Keras, MobileNetV2, Transfer Learning, OpenCV, Pandas}
\begin{itemize}\footnotesize
  \item Built a medical image ML pipeline for MRI brain tumor detection, achieving \textbf{86.6\%} accuracy with documented methodology and reproducible code.
  \item Applied model compression via fine-tuning to balance accuracy against resource constraints, generating confusion matrices and loss curves to support interpretability.
\end{itemize}

\vspace{2pt}

\roleheading{AI Sales Forecasting \& Inventory Management}{\href{https://github.com/jonathanrao99}{GitHub}}
\toolsline{Python, TensorFlow/Keras, LSTM, Scikit-learn, Flask, SQL, Pandas}
\begin{itemize}\footnotesize
  \item Trained an LSTM time-series forecasting model with normalization, feature engineering, and cross-validation, achieving $\sim$\textbf{92\%} accuracy.
\end{itemize}

% ── EDUCATION ─────────────────────────────────────────────────────
\section{Education}

\roleheading{Texas A\&M University -- Victoria}{Jan 2025 -- May 2026}
\orgline{M.S. Data Science \;|\; GPA: 3.8 / 4.0}{Houston, TX}
\vspace{1pt}
\footnotesize\textit{Data Mining, Machine Learning, Data Warehousing, Advanced SQL, Statistical Modeling, Data Visualization}

\end{document}
